---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# feh

<!-- badges: start -->
<!-- badges: end -->

Flap flap flap...flap flap flap...feeeeeeehhhh. Helloooooo summonerssssss.

## Installation

You can install the development version of feh like so:

``` r
# FILL THIS IN! HOW CAN PEOPLE INSTALL YOUR DEV PACKAGE?
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(feh)
## basic example code
set.seed(1)

sesh <- session(matrix(c(15,27,25,0,
                 12,23,17,1,
                 9,18,12,1,
                 13,23,16,2),4,4,byrow=T), 
        baserate=0.03, rateups=0, targetcol="Red", targetrar="5*F")

print(sesh)
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this. You could also use GitHub Actions to re-render `README.Rmd` every time you push. An example workflow can be found here: <https://github.com/r-lib/actions/tree/v1/examples>.

You can also embed plots, for example:

```{r, echo = FALSE}
url_owl <- "http://gamepedia.cursecdn.com/feheroes_gamepedia_en/2/23/Feh_BtlFace_C.png"

knitr::include_graphics(url_owl)
```


In that case, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
